### 2017-06-27 paper/example.tex
cleaned

%==========================================
%
% Sibgrapi 2015 paper
%
%==========================================

% Note that the a4paper option is mainly intended so that authors in
% countries using A4 can easily print to A4 and see how their papers will
% look in print - the typesetting of the document will not typically be
% affected with changes in paper size (but the bottom and side margins will).
% Use the testflow package mentioned above to verify correct handling of
% both paper sizes by the user's LaTeX system.
%
% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
% should be used if it is desired that the figures are to be displayed in
% draft mode.
%
\documentclass[10pt, conference]{IEEEtran}

% *** MISC UTILITY PACKAGES ***
%
%\usepackage{ifpdf}
% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
% compilation based on whether the output is pdf or dvi.
% usage:
% \ifpdf
%   % pdf code
% \else
%   % dvi code
% \fi
% The latest version of ifpdf.sty can be obtained from:
% http://www.ctan.org/tex-archive/macros/latex/contrib/oberdiek/
% Also, note that IEEEtran.cls V1.7 and later provides a builtin
% \ifCLASSINFOpdf conditional that works the same way.
% When switching from latex to pdflatex and vice-versa, the compiler may
% have to be run twice to clear warning/error messages.

% *** CITATION PACKAGES ***
%
%\usepackage{cite}
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 4.0 (2003-05-27) and later if using hyperref.sty. cite.sty does
% not currently provide for hyperlinked citations.
% The latest version can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/cite/
% The documentation is contained in the cite.sty file itself.

% *** GRAPHICS RELATED PACKAGES ***
%
\usepackage{subimages}
\setfigdir{figs}

% *** MATH PACKAGES ***
%
\usepackage[cmex10]{amsmath}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics. If using
% it, be sure to load this package with the cmex10 option to ensure that
% only type 1 fonts will utilized at all point sizes. Without this option,
% it is possible that some math symbols, particularly those within
% footnotes, will be rendered in bitmap form which will result in a
% document that can not be IEEE Xplore compliant!
%
% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/
\usepackage{amsthm}
\newtheorem{definition}{Definition}

% *** SPECIALIZED LIST PACKAGES ***
%
%\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithms/
% There is also a support site at:
% http://algorithms.berlios.de/index.html
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithmicx/

% *** ALIGNMENT PACKAGES ***
%
%\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/tools/

%\usepackage{mdwmath}
%\usepackage{mdwtab}
% Also highly recommended is Mark Wooding's extremely powerful MDW tools,
% especially mdwmath.sty and mdwtab.sty which are used to format equations
% and tables, respectively. The MDWtools set is already installed on most
% LaTeX systems. The lastest version and documentation is available at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/mdwtools/

% IEEEtran contains the IEEEeqnarray family of commands that can be used to
% generate multiline equations as well as matrices, tables, etc., of high
% quality.

%\usepackage{eqparbox}
% Also of notable interest is Scott Pakin's eqparbox package for creating
% (automatically sized) equal width boxes - aka "natural width parboxes".
% Available at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/eqparbox/

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
\usepackage{hyperref}

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Example of IEEEtran.cls, adapted for Sibgrapi 2015}

%------------------------------------------------------------------------- 
% change the % on next lines to produce the final camera-ready version 
\newif\iffinal
%\finalfalse
\finaltrue
\newcommand{\jemsid}{99999}
%-------------------------------------------------------------------------

% author names and affiliations
% use a multiple column layout for up to two different
% affiliations

\iffinal
  \author{%
    \IEEEauthorblockN{Bruno Iochins Grisci}
    \IEEEauthorblockA{%
      line 1 (of Affiliation): Instituto de Informatica\\
      line 2: UFRGS\\
      line 3: Porto Alegre, Brazil\\
      line 4: Email:  \href{mailto:bigrisci@inf.ufrgs.br}{bigrisci@inf.ufrgs.br}}
  \and
    \IEEEauthorblockN{Authors Name/s per 2nd Affiliation}
    \IEEEauthorblockA{%
      line 1 (of Affiliation): dept. name of organization\\
      line 2: name of organization, acronyms acceptable\\
      line 3: City, Country\\
      line 4: }
  }
\else
  \author{Sibgrapi paper ID: \jemsid \\ }
\fi

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
% 
%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
%Homer Simpson\IEEEauthorrefmark{2},
%James Kirk\IEEEauthorrefmark{3}, 
%Montgomery Scott\IEEEauthorrefmark{3} and
%Eldon Tyrell\IEEEauthorrefmark{4}}
%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
%Georgia Institute of Technology,
%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
%Email: homer@thesimpsons.com}
%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
%Telephone: (800) 555--1212, Fax: (888) 555--1212}
%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}

%------------------------------------------------------------------------- 
% Special Sibgrapi teaser
\teaser{%
  \oneimage{Teasing result of our method: from this data input (left), the relevant feature are extracted using our technique (middle), producing effective result (right).}{.99}{sibgrapi.png}
}
%-------------------------------------------------------------------------

% make the title area
\maketitle

\begin{abstract}
With the recent evolution of certain applications, there is a growing need for methods of this kind\ldots{}

This paper proposes exactly the right solution for this sub-problem in terms of several criterions. It introduces techniques for this and that tasks, improving this characteristic of the results. It further opens to a wider range of applications, as the experiments related in this paper confirms.

% DO NOT USE SPECIAL CHARACTERS, SYMBOLS, OR MATH IN YOUR TITLE OR ABSTRACT.
%
\end{abstract}

\begin{IEEEkeywords}
one or two words; separated by semicolon; from specific; to generic fields;

\end{IEEEkeywords}

\IEEEpeerreviewmaketitle

% Wherever Times is specified, Times Roman or Times New Roman may be used. If neither is available on your system, please use the font closest in appearance to Times. Avoid using bit-mapped fonts if possible. True-Type 1 or Open Type fonts are preferred. Please embed symbol fonts, as well, for math, etc.

%==========================================
%==========================================

%==========================================
\section{Introduction}
%
In the general context of this field, a certain kind of application has recently aggregated values for the following reasons.
%
However, existing approaches to produce good results for this application do not perform optimally yet, being limited to certain aspects and requiring too much resources to be actually used.

%------------------------------------------------------------------------- 
\paragraph*{Contributions}
%
This paper proposes a different approach to overcome those difficulties. By introducing and adapting those techniques to this context, we achieve significant improvements on the recent results. In particular, our method can handle this kind of data, and reduces the resource requirements. In our experiments, we evaluate a gain of $xx\%$ and could observe several interesting results that validate and delimit our approach.

%------------------------------------------------------------------------- 
\subsection{Related work}
%
We can roughly classify the approaches used for our application in three categories: first category, second category, and last category.\\
Approaches in the first category were introduced by Pierre~\cite{Sibgrapi2015} using this and that techniques.

\subimages[htb]{Technique overview}{overview}{%
  \subimage[First step]{.31}{sibgrapi}%
  \subimage[Second step]{.31}{sibgrapi}%
  \subimage[Result]{.31}{sibgrapi}%
}
%------------------------------------------------------------------------- 
\subsection{Technique overview}
%
In order to produce this application, we start with this processing, followed by this technique. In order to cope with this challenge, we introduce this formulation to produce this intermediate result. The formulation leads to this type of system, which is efficiently solved by adapting this technique. The final result is produced by this transform. The whole process is schematized in \figref{overview}.

%==========================================
\section{Technical background}
%
In this section, we detail this classical technique. The reader can find a more complete exposition in the work of Paul~\cite{Sibgrapi2015}.

%------------------------------------------------------------------------- 
\subsection{Important concept}
%
An \emph{important concept} is a type of object:
\begin{definition}[Important concept]
Given this and that, an object $X$ is an important concept if it respects the following properties\ldots{}
\end{definition}

%------------------------------------------------------------------------- 
\subsection{Usual adaptation}
%
This concept has been used for applications similar to ours~\cite{Sibgrapi2015}, using the following formulation\ldots{}

%==========================================
\section{New technique or technique adaptation}
\label{sec:technique}
%
Our technique aims at obtaining that result. It particularly suits to the problem since it is formulated as\ldots{}

%------------------------------------------------------------------------- 
\subsection{Formulation}

%------------------------------------------------------------------------- 
\subsection{Solution}

%------------------------------------------------------------------------- 
\subsection{Initialization and tuning}

%==========================================
\section{Implementation}
%
In order to reduce the resources needed for our method, we use the following implementation strategy.

%------------------------------------------------------------------------- 
\subsection{Solver}

%------------------------------------------------------------------------- 
\subsection{Result display}

%==========================================
\section{Experiments}
%
We validate our technique through a series of experiments.

%------------------------------------------------------------------------- 
\paragraph*{First experiment}
%
The first experiment checks this aspect of our method on perfect examples.

%------------------------------------------------------------------------- 
\paragraph*{Second experiment}
%
The second experiment checks the speedup obtained by the implementation strategy compared to previous technique~\cite{Sibgrapi2015}.

%------------------------------------------------------------------------- 
\paragraph*{Third experiment}
%
The last experiment test our method on real data.

%==========================================
\section{Results and Discussion}
%
We performed the above-mentioned experiments on the following type of data: \ldots{} For each data, we used the following tuning parameters of our method.

\begin{table}
\caption{Performances results: timings are expressed in milliseconds.}
\label{tab:perfs}
\centering
\begin{tabular}{lr|rr|c}
\multicolumn{1}{c}{\bf Data} &
\multicolumn{1}{c|}{\bf Size} &
\multicolumn{1}{c}{\bf Ours} &
\multicolumn{1}{c|}{\bf Previous} &
\multicolumn{1}{c}{\bf Gain} \\ \hline
Data 1	&        50 	& 0.1 &     1 000	& x$10^3$ \\
Data 2	&      100 	& 0.2 &     2 000	& x$10^3$ \\
Data 3	&      500 	& 0.8 &   10 000	& x$10^3$ \\
Data 4	&   1 000 	& 1.2 &   20 000	& x$10^3$ \\
Data 5	&   5 000 	& 1.9 & 100 000	& x$10^4$ \\
Data 6	& 10 000 	& 2.1 & 200 000	& x$10^4$
\end{tabular}
\end{table}
%
%------------------------------------------------------------------------- 
\subsection{Performances}
%
We report on Table~\ref{tab:perfs} the performances of our technique on a computer at xxGhz with this graphic card.
We observe that our technique outperforms previous approaches on this kind of data, and an equivalent result on this other kind of data.

\subimages[htb]{Quality assessment}{quality}{
  \subimage{.48}{sibgrapi}%
  \subimage{.48}{sibgrapi}%
}

%------------------------------------------------------------------------- 
\subsection{Quality}
%
As observed on \figref{quality}, our method achieve good results in this situation. 
This can be measured by this criterion, and the results are reported on Table~\ref{tab:quality}.

\begin{table}
\caption{Quality measures: timings are expressed in milliseconds.}
\label{tab:quality}
\centering
\begin{tabular}{l|r|r}
\multicolumn{1}{c}{\bf Images} &
\multicolumn{1}{c|}{\bf PSNR} &
\multicolumn{1}{c}{\bf  MSE} \\ \hline
Image 1	&  40.2	& 0.02 \\
Image 2	&  30.9	& 1.02 \\
Image 3 &  20.1 & 0.18 \\
\end{tabular}
\end{table}

%------------------------------------------------------------------------- 
\subsection{Limitation}
%
As mentioned in Section~\ref{sec:technique}, we expect our method to suit better this kind of data. On the other kind, this particularity does not fit into our formulation for this and that reason. Indeed, this can be observed in the results of \figref{quality}. 
We plan to improve for that kind of data in future work. However, our technique performed well on this data, which does not respect our condition, since this other aspect reduced the negative impact of its characteristic.

%==========================================
\section{Conclusion}
%
In this paper, we introduced this technique and showed that it is particularly appropriate for that application. We obtained this and that improvements, and plan to extend this application in that direction in future work.

%==========================================
\iffinal
% use section* for acknowledgement
\section*{Acknowledgment}
%
The authors would like to thank this colleague and this financing institute.
\fi

%==========================================

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

\bibliographystyle{IEEEtran}
\bibliography{example}

\end{document}

### 2017-06-27 paper/paper.tex
cleaned

--- 2017-06-27 paper/example.tex
@@
 % can use linebreaks \\ within to get better formatting as desired
-\title{Example of IEEEtran.cls, adapted for Sibgrapi 2015}
+\title{Visualization tool for comparison of mutations in protein simulations}
 
@@
     \IEEEauthorblockA{%
-      line 1 (of Affiliation): Instituto de Informatica\\
-      line 2: UFRGS\\
-      line 3: Porto Alegre, Brazil\\
-      line 4: Email:  \href{mailto:bigrisci@inf.ufrgs.br}{bigrisci@inf.ufrgs.br}}
-  \and
-    \IEEEauthorblockN{Authors Name/s per 2nd Affiliation}
-    \IEEEauthorblockA{%
-      line 1 (of Affiliation): dept. name of organization\\
-      line 2: name of organization, acronyms acceptable\\
-      line 3: City, Country\\
-      line 4: }
+      Instituto de Informatica\\
+      UFRGS\\
+      Porto Alegre, Brazil\\
+      Email:  \href{mailto:bigrisci@inf.ufrgs.br}{bigrisci@inf.ufrgs.br}}
   }
@@
 %==========================================
+ %1) Introdução (motivação para o trabalho, objetivos e resultados esperados), 2) Caracterização dos dados e problema/questões que a visualização pretende responder, 3) Descrição da técnica de visualização desenvolvida (incluir aqui informação sobre a implementação, biblioteca ou ferramenta utilizada), 4) Resultados (exemplos de uso), 5) Conclusões.
+Não há limite de páginas, mas o razoável é de 8 a 12 páginas no máximo.
 
@@
 
-%------------------------------------------------------------------------- 
-\paragraph*{Contributions}
-%
-This paper proposes a different approach to overcome those difficulties.
-By introducing and adapting those techniques to this context, we achieve significant improvements on the recent results.
-In particular, our method can handle this kind of data, and reduces the resource requirements.
-In our experiments, we evaluate a gain of $xx\%$ and could observe several interesting results that validate and delimit our approach.
-
-%------------------------------------------------------------------------- 
 \subsection{Related work}
@@
 }
+
+%==========================================
+\section{Data characterization}
+
+\subsection{Data dimensions}
+
+\paragraph*{DSSP}
+%
+The first experiment checks this aspect of our method on perfect examples.
+
+\paragraph*{SASA}
+%
+The first experiment checks this aspect of our method on perfect examples.
+
+\paragraph*{GYRATE}
+%
+The first experiment checks this aspect of our method on perfect examples.
+
+\paragraph*{ENERGY}
+%
+The first experiment checks this aspect of our method on perfect examples.
+
+\paragraph*{RMSF}
+%
+The first experiment checks this aspect of our method on perfect examples.
+
+%==========================================
+\section{Technical background}
+%
+In this section, we detail this classical technique. The reader can find a more complete exposition in the work of Paul~\cite{Sibgrapi2015}.
+
 %------------------------------------------------------------------------- 
-\subsection{Technique overview}
+\section{Technique overview}
 %
@@
 
-%==========================================
-\section{Technical background}
-%
-In this section, we detail this classical technique. The reader can find a more complete exposition in the work of Paul~\cite{Sibgrapi2015}.
+\subsection{Grid}
+\paragraph*{Item highlighting}
+\paragraph*{Item selection}
 
-%------------------------------------------------------------------------- 
-\subsection{Important concept}
-%
-An \emph{important concept} is a type of object:
-\begin{definition}[Important concept]
-Given this and that, an object $X$ is an important concept if it respects the following properties\ldots{}
-\end{definition}
+\subsection{Parallel Coordinates}
 
-%------------------------------------------------------------------------- 
-\subsection{Usual adaptation}
-%
-This concept has been used for applications similar to ours~\cite{Sibgrapi2015}, using the following formulation\ldots{}
+\paragraph*{Axis brushing}
+\paragraph*{Axis sorting}
+\paragraph*{Axis reordering}
+\paragraph*{Recoloring by axis selection}
 
-%==========================================
-\section{New technique or technique adaptation}
-\label{sec:technique}
-%
-Our technique aims at obtaining that result. It particularly suits to the problem since it is formulated as\ldots{}
+\subsection{Radar Plot}
+\paragraph*{Item highlighting}
 
-%------------------------------------------------------------------------- 
-\subsection{Formulation}
-
-%------------------------------------------------------------------------- 
-\subsection{Solution}
-
-%------------------------------------------------------------------------- 
-\subsection{Initialization and tuning}
-
-%==========================================
-\section{Implementation}
-%
-In order to reduce the resources needed for our method, we use the following implementation strategy.
-
-%------------------------------------------------------------------------- 
-\subsection{Solver}
-
-%------------------------------------------------------------------------- 
-\subsection{Result display}
+\subsection{Slider}
 
@@
 We validate our technique through a series of experiments.
-
-%------------------------------------------------------------------------- 
-\paragraph*{First experiment}
-%
-The first experiment checks this aspect of our method on perfect examples.
-
-%------------------------------------------------------------------------- 
-\paragraph*{Second experiment}
-%
-The second experiment checks the speedup obtained by the implementation strategy compared to previous technique~\cite{Sibgrapi2015}.
-
-%------------------------------------------------------------------------- 
-\paragraph*{Third experiment}
-%
-The last experiment test our method on real data.
 
@@
 %------------------------------------------------------------------------- 
-\subsection{Limitation}
+\subsection{Future work}
 %

### 2017-06-28 radar-chart/radarChart.js
updated radar plot

@@ -1,272 +1,1081 @@
-/////////////////////////////////////////////////////////
-/////////////// The Radar Chart Function ////////////////
-/////////////// Written by Nadieh Bremer ////////////////
-////////////////// VisualCinnamon.com ///////////////////
-/////////// Inspired by the code of alangrafu ///////////
-/////////////////////////////////////////////////////////
-	
-function RadarChart(id, data, options) {
-	var cfg = {
-	 w: 600,				//Width of the circle
-	 h: 600,				//Height of the circle
-	 margin: {top: 20, right: 20, bottom: 20, left: 20}, //The margins of the SVG
-	 levels: 3,				//How many levels or inner circles should there be drawn
-	 maxValue: 0, 			//What is the value that the biggest circle will represent
-	 labelFactor: 1.25, 	//How much farther than the radius of the outer circle should the labels be placed
-	 wrapWidth: 60, 		//The number of pixels after which a label needs to be given a new line
-	 opacityArea: 0.35, 	//The opacity of the area of the blob
-	 dotRadius: 4, 			//The size of the colored circles of each blog
-	 opacityCircles: 0.1, 	//The opacity of the circles of each blob
-	 strokeWidth: 2, 		//The width of the stroke around each blob
-	 roundStrokes: false,	//If true the area and stroke will follow a round path (cardinal-closed)
-	 color: d3.scale.category10()	//Color function
-	};
-	
-	//Put all of the options into a variable called cfg
-	if('undefined' !== typeof options){
-	  for(var i in options){
-		if('undefined' !== typeof options[i]){ cfg[i] = options[i]; }
-	  }//for i
-	}//if
-	
-	//If the supplied maxValue is smaller than the actual one, replace by the max in the data
-	var maxValue = Math.max(cfg.maxValue, d3.max(data, function(i){return d3.max(i.map(function(o){return o.value;}))}));
-		
-	var allAxis = (data[0].map(function(i, j){return i.axis})),	//Names of each axis
-		total = allAxis.length,					//The number of different axes
-		radius = Math.min(cfg.w/2, cfg.h/2), 	//Radius of the outermost circle
-		Format = d3.format('%'),			 	//Percentage formatting
-		angleSlice = Math.PI * 2 / total;		//The width in radians of each "slice"
-	
-	//Scale for the radius
-	var rScale = d3.scale.linear()
-		.range([0, radius])
-		.domain([0, maxValue]);
-		
[…]

### 2017-06-29 paper/paper.tex
paper

@@
 % can use linebreaks \\ within to get better formatting as desired
-\title{Visualization tool for comparison of mutations in protein simulations}
+\title{Visualization tool for comparison of amino acids in protein simulations}
 
@@
 \begin{abstract}
-With the recent evolution of certain applications, there is a growing need for methods of this kind\ldots{}
-
-This paper proposes exactly the right solution for this sub-problem in terms of several criterions.
-It introduces techniques for this and that tasks, improving this characteristic of the results.
-It further opens to a wider range of applications, as the experiments related in this paper confirms.
 
@@
 %
-In the general context of this field, a certain kind of application has recently aggregated values for the following reasons.
-%
-However, existing approaches to produce good results for this application do not perform optimally yet, being limited to certain aspects and requiring too much resources to be actually used.
 
@@
 %
-We can roughly classify the approaches used for our application in three categories: first category, second category, and last category.\\
-Approaches in the first category were introduced by Pierre~\cite{Sibgrapi2015} using this and that techniques.
 
@@
 %
-The first experiment checks this aspect of our method on perfect examples.
 
@@
 %
-We validate our technique through a series of experiments.
 
@@
 %
-We performed the above-mentioned experiments on the following type of data: \ldots{} For each data, we used the following tuning parameters of our method.
 
-\begin{table}
-\caption{Performances results: timings are expressed in milliseconds.}
-\label{tab:perfs}
-\centering
-\begin{tabular}{lr|rr|c}
-\multicolumn{1}{c}{\bf Data} &
-\multicolumn{1}{c|}{\bf Size} &
-\multicolumn{1}{c}{\bf Ours} &
-\multicolumn{1}{c|}{\bf Previous} &
-\multicolumn{1}{c}{\bf Gain} \\ \hline
-Data 1	&        50 	& 0.1 &     1 000	& x$10^3$ \\
-Data 2	&      100 	& 0.2 &     2 000	& x$10^3$ \\
-Data 3	&      500 	& 0.8 &   10 000	& x$10^3$ \\
-Data 4	&   1 000 	& 1.2 &   20 000	& x$10^3$ \\
-Data 5	&   5 000 	& 1.9 & 100 000	& x$10^4$ \\
-Data 6	& 10 000 	& 2.1 & 200 000	& x$10^4$
-\end{tabular}
-\end{table}
 %
-%------------------------------------------------------------------------- 
-\subsection{Performances}
-%
-We report on Table~\ref{tab:perfs} the performances of our technique on a computer at xxGhz with this graphic card.
-We observe that our technique outperforms previous approaches on this kind of data, and an equivalent result on this other kind of data.
-
-\subimages[htb]{Quality assessment}{quality}{
-  \subimage{.48}{sibgrapi}%
-  \subimage{.48}{sibgrapi}%
-}
-
-%------------------------------------------------------------------------- 
-\subsection{Quality}
-%
-As observed on \figref{quality}, our method achieve good results in this situation. 
-This can be measured by this criterion, and the results are reported on Table~\ref{tab:quality}.
-
-\begin{table}
-\caption{Quality measures: timings are expressed in milliseconds.}
-\label{tab:quality}
-\centering
-\begin{tabular}{l|r|r}
-\multicolumn{1}{c}{\bf Images} &
-\multicolumn{1}{c|}{\bf PSNR} &
-\multicolumn{1}{c}{\bf  MSE} \\ \hline
-Image 1	&  40.2	& 0.02 \\
-Image 2	&  30.9	& 1.02 \\
-Image 3 &  20.1 & 0.18 \\
-\end{tabular}
-\end{table}
 
@@
 %
-As mentioned in Section~\ref{sec:technique}, we expect our method to suit better this kind of data.
-On the other kind, this particularity does not fit into our formulation for this and that reason.
-Indeed, this can be observed in the results of \figref{quality}.
-We plan to improve for that kind of data in future work.
-However, our technique performed well on this data, which does not respect our condition, since this other aspect reduced the negative impact of its characteristic.
 
@@
 %
-In this paper, we introduced this technique and showed that it is particularly appropriate for that application.
-We obtained this and that improvements, and plan to extend this application in that direction in future work.
 

### 2017-06-29 paper/paper.tex
paper figs
paper

@@
 % can use linebreaks \\ within to get better formatting as desired
-\title{Visualization tool for comparison of amino acids in protein simulations}
+\title{Visualization tool for comparison of a single amino acid change in protein simulation}
 
@@
 \teaser{%
-  \oneimage{Teasing result of our method: from this data input (left), the relevant feature are extracted using our technique (middle), producing effective result (right).}{.99}{sibgrapi.png}
+  \oneimage{Image of the tool with all elements presented.}{.99}{all.png}
 }

### 2017-06-30 paper/paper.tex
paper demo

@@
 
+Proteins are polymers formed by a sequence of 20 different possible amino acids that under physiological conditions fold into a precise shape known as its native state~\cite{anfinsen:1973}.
+Each amino acid has an alpha carbon (\texttt{CA}) with bonds to amino (\texttt{NH2}) and carboxyl (\texttt{COOH}) groups and a variable side-chain (\texttt{R}) that determines the particular physicochemical properties of each residue.
+A peptide is a molecule composed of two or more amino acids chained by a chemical bond called the \textit{peptide bond}.
+This bond is formed when the carboxyl group of one residue reacts with the amino group of the other residue, releasing a water molecule.
+The interaction between amino acids in a protein causes the polypeptide chain to fold, usually in a proper configuration, as \texttt{$\alpha$-helix}, \texttt{$\beta$-sheet}, \texttt{coil} or \texttt{turn}.
+These local folding patterns represent the secondary structure of a protein.
+The topology or fold is given by the succession of secondary structures connected in a \texttt{3D} space.
+The specific characteristics of the peptide bond have significant implications for the \texttt{3D} fold that can be adopted by polypeptides.
+The peptide bond (\texttt{C-N}) has a double bond, and it is not allowed rotation of the molecule around this bond.
+The rotation is only permitted around the bonds \texttt{N-C$\alpha$} and \texttt{C}$_{\alpha}$\texttt{-C}.
+The analysis of experimental protein structures (\texttt{X}-ray data) reveals that amino acid residues can assume many conformations in proteins~\cite{Borguesan:2015}.
+Each amino acid has a set of physiochemical properties which contributes to its intrinsic conformational preference~\cite{Mathura:2005}.
+Amino acids in a secondary structure usually adopt a particular set of backbone torsion angles~\cite{Borguesan:2015}.
+
 \subsection{Related work}
@@
 
-\subimages[htb]{Technique overview}{overview}{%
-  \subimage[First step]{.31}{sibgrapi}%
-  \subimage[Second step]{.31}{sibgrapi}%
-  \subimage[Result]{.31}{sibgrapi}%
-}
+%\subimages[htb]{Technique overview}{overview}{%
+%  \subimage[First step]{.31}{sibgrapi}%
+%  \subimage[Second step]{.31}{sibgrapi}%
+%  \subimage[Result]{.31}{sibgrapi}%
+%}
 
@@
 %
-In this section, we detail this classical technique. The reader can find a more complete exposition in the work of Paul~\cite{Sibgrapi2015}.
 
@@
 %
-In order to produce this application, we start with this processing, followed by this technique.
-In order to cope with this challenge, we introduce this formulation to produce this intermediate result.
-The formulation leads to this type of system, which is efficiently solved by adapting this technique.
-The final result is produced by this transform.
-The whole process is schematized in \figref{overview}.
 
 \subsection{Grid}
+\begin{figure}
+\includegraphics[width=0.8\linewidth]{figs/grid.png}
+\caption{Overview of the used grid.} 
+\label{fig:grid}
+\end{figure}
 \paragraph*{Item highlighting}
@@
 \subsection{Parallel Coordinates}
+\begin{figure}
+\includegraphics[width=0.8\linewidth]{figs/brush.png}
+\caption{Example of the use of brush.} 
+\label{fig:brush}
+\end{figure}
+\paragraph*{Axis brushing} Fig.~\ref{fig:brush}
 
-\paragraph*{Axis brushing}
 \paragraph*{Axis sorting}
@@
 \subsection{Radar Plot}
+\begin{figure}
+\includegraphics[width=0.8\linewidth]{figs/radar.png}
+\caption{Example of one amino acid being visualized in the radar plot.} 
+\label{fig:radar}
+\end{figure}
 \paragraph*{Item highlighting}
@@
 %
+A demo can be tested at: http://inf.ufrgs.br/~bigrisci/parallel-coordinates/examples/table.html
 
@@
 %
-The authors would like to thank this colleague and this financing institute.
+
 \fi
@@
 \bibliographystyle{IEEEtran}
-\bibliography{example}
+\bibliography{my}
 

### 2017-06-30 radar-chart/radarChart.js
radar plot axis reordering

@@ -94,7 +94,8 @@ function RadarChart() {
       'gridCircle': { 'mouseover': null, 'mouseout': null, 'mouseclick': null },
       'axisLabel': { 'mouseover': null, 'mouseout': null, 'mouseclick': null },
       'line': { 'mouseover': null, 'mouseout': null, 'mouseclick': null },
-      'legend': { 'mouseover': legendMouseover, 'mouseout': areaMouseout, 'mouseclick': legendClick },
+      //'legend': { 'mouseover': legendMouseover, 'mouseout': areaMouseout, 'mouseclick': legendClick },
+      'legend': { 'mouseover': legendMouseover, 'mouseout': areaMouseout },
       'axisLegend': { 'mouseover': null, 'mouseout': null, 'mouseclick': null },
       'radarArea': { 'mouseover': areaMouseover, 'mouseout': areaMouseout, 'mouseclick': null },
       'radarInvisibleCircle': { 'mouseover': tooltip_show, 'mouseout': tooltip_hide, 'mouseclick': null }
@@ -974,12 +975,12 @@ function RadarChart() {
             });	
 	}
 
-   function legendClick(d, i, self) {
+   /*function legendClick(d, i, self) {
          var keys = _data.map(function(m) {return m.key});
          modifyList(options.areas.filter, keys[d], keys);
          legend_toggles[d] = legend_toggles[d] ? false : true;
          update();
-   }
+   }*/
 
    function tooltip_show(d, i, self) {
          if (legend_toggles[d._i]) return;

### 2017-07-17 paper/paper.tex
paper

@@
 
+The amino acids sequence of a protein is directly related to its structure in three dimensional space, which is defining of the protein biological function.
+The change of only one amino acid in the chain is capable of great modification of the structure and function of a protein because of the differences in size and physical-chemical properties among amino acids~\cite{nelson2008lehninger}.
+
 \subsection{Related work}
 %
-
-%\subimages[htb]{Technique overview}{overview}{%
-%  \subimage[First step]{.31}{sibgrapi}%
-%  \subimage[Second step]{.31}{sibgrapi}%
-%  \subimage[Result]{.31}{sibgrapi}%
-%}
 
@@
 
+The data for testing this visualization tool comes from the Kappa-conotoxin PVIIA, with amino acids sequence: $CRIPNQKCFQHLDDCCSRKCNRFNKCV$.
+Kappa-conotoxins are neurotoxical proteins extracted from sea slugs poison.
+They are inhibitors of the potassium channel and when injected in different organisms some alterations in their effect can be observed, from hyperactivity in fish to death when combined with other variants of conotoxins.
+The substitution of the asparagine ($N$) in the fifth position in the amino acids chain of the Kappa-conotoxin PVIIA by an alanine ($A$) is know to cause a reduction of 100\% in the toxicity of this protein~\cite{jacobsen2000single}~\cite{mir2016conotoxins}~\cite{akey2002inherited}.
+
+For this study, this asparagine was changed by all possible 20 amino acids, and for each resulting structure a molecular dynamics simulation was performed in order to evaluate its behavior during a predetermined period of time under chosen conditions.
+The simulations were performed with GROMACS~\cite{hess2008gromacs}, a software for biomolecules simulation, with the simulated time of 50ns.
+These simulations mimic the behavior of biomolecules in a solvent under controled temperature.
+From the data created versus time, the following attributes were studied.
+
 \subsection{Data dimensions}
 
-\paragraph*{DSSP}
+\paragraph*{DSSP} Analysis of the secondary structure of the protein for each frame of the simulation.
+The secondary structure is a local structural conformation of a region in the amino acids sequence which follows specific patterns that, once folded, will originate the three dimensional functional structure of the protein.
 %
 
-\paragraph*{SASA}
+\paragraph*{SASA} Solvent-accessible surface area is the surface area of the protein that is accessible to the solvent.
+By analysing the area exposed to the solvent, i.e., what is around the protein, it is possible to infer how denatured is the protein, so the greater the SASA value, the greater the denaturation.
 %
 
-\paragraph*{GYRATE}
+\paragraph*{GYRATE} The radius of gyration can be used as a measurement of the compactness of a protein structure.
+It describes the overall spread of the molecule and is calculated taking the root mean square distance of the atoms from their common centre of gravity.
+Greater values of radius of gyration means a less compact protein.
 %
 
-\paragraph*{ENERGY}
+\paragraph*{ENERGY} This attribute measures the total energy of the system.
+The energy is a stability indicator, usually comparable, in which systems with less energy will be more stable (less entropy).
 %
 
-\paragraph*{RMSF}
+\paragraph*{RMSF} The root mean square fluctuation of atomic positions is the measure of the average distance between the atoms of the simulated protein and a well-defined average position. 
 %
+
+All the dimensions are continuous numerical values. As can be seen, the data of a single simulation is multidimensional and changes over the simulated time.
 
@@
 %
-A demo can be tested at: http://inf.ufrgs.br/~bigrisci/parallel-coordinates/examples/table.html
+A demo can be tested at: http://inf.ufrgs.br/~bigrisci/parallel-coordinates/
 

### 2017-07-31 paper/paper.tex
paper

@@
 \paragraph*{DSSP} Analysis of the secondary structure of the protein for each frame of the simulation.
-The secondary structure is a local structural conformation of a region in the amino acids sequence which follows specific patterns that, once folded, will originate the three dimensional functional structure of the protein.
+The secondary structure is a local structural conformation of a region in the amino acids sequence which follows specific patterns that, once folded, will originate the three dimensional functional structure of the protein~\cite{kabsch1983dictionary}.
 %
@@
 \paragraph*{SASA} Solvent-accessible surface area is the surface area of the protein that is accessible to the solvent.
-By analysing the area exposed to the solvent, i.e., what is around the protein, it is possible to infer how denatured is the protein, so the greater the SASA value, the greater the denaturation.
+By analysing the area exposed to the solvent, i.e., what is around the protein, it is possible to infer how denatured is the protein, so the greater the SASA value, the greater the denaturation~\cite{richmond1984solvent}.
 %
@@
 It describes the overall spread of the molecule and is calculated taking the root mean square distance of the atoms from their common centre of gravity.
-Greater values of radius of gyration means a less compact protein.
+Greater values of radius of gyration means a less compact protein~\cite{lobanov2008radius}.
 %
@@
 \paragraph*{ENERGY} This attribute measures the total energy of the system.
-The energy is a stability indicator, usually comparable, in which systems with less energy will be more stable (less entropy).
+The energy is a stability indicator, usually comparable, in which systems with less energy will be more stable (less entropy)~\cite{van1998gromos}.
 %
 
-\paragraph*{RMSF} The root mean square fluctuation of atomic positions is the measure of the average distance between the atoms of the simulated protein and a well-defined average position. 
+\paragraph*{RMSF} The root mean square fluctuation of atomic positions is the measure of the average distance between the atoms of the simulated protein and a well-defined average position~\cite{maiorov1994significance}.
 %
@@
 
+\subsection{Grid}
+
+\subsection{Parallel Coordinates}
+
+\subsection{Radar Plot}
+
 %------------------------------------------------------------------------- 
@@
 
+The proposed visualization technique takes advantage of the use of three different visualization tools working in synchrony, and the capability of changing the data over time.
+
 \subsection{Grid}
+
+The grid is an interactive table where the raw values of the data are displayed as in Fig.~\ref{fig:grid}.
+Its function is to provide a place where the data can be observed with more detail for scientific purposes.
+
 \begin{figure}
-\includegraphics[width=0.8\linewidth]{figs/grid.png}
+\includegraphics[width=0.9\linewidth]{figs/grid.png}
 \caption{Overview of the used grid.} 
@@
 \end{figure}
-\paragraph*{Item highlighting}
-\paragraph*{Item selection}
+\paragraph*{Item highlighting} When hoving the mouse over a line in the grid, that line is highlited. This operation also reflects on the other plots.
+\paragraph*{Item selection} When right-clicking on a line of the grid with the mouse that line is selected and the item is fixed on the plots.
 
 \subsection{Parallel Coordinates}
+
+The parallel coordinates plot is used to show a global view of the data, displaying all the itens in a given time at once.
+
 \begin{figure}
-\includegraphics[width=0.8\linewidth]{figs/brush.png}
-\caption{Example of the use of brush.} 
+\includegraphics[width=1.0\linewidth]{figs/brush.png}
+\caption{Example of use of the brush.} 
 \label{fig:brush}
 \end{figure}
-\paragraph*{Axis brushing} Fig.~\ref{fig:brush}
+\paragraph*{Axis brushing} The brush is the filtering operation of the parallel coordinates and can be seen in Fig.~\ref{fig:brush}.
+Draging the mouse along an axis select the itens in that range.
+This change is reflected on the grid.
+\paragraph*{Axis sorting} When double clicking an axis the order of its values is inverted. This change is reflected on the radar plot.
+\paragraph*{Axis reordering} When right-clicking an axis and draging it to left or right the axes are reordered. This change is reflected on the radar plot.
+\paragraph*{Recoloring by axis selection} The color of the lines of the parallel coordinates is defined by the range of the selected axis.
+Clicking an axis change the dimension used for coloring.
+Figures~\ref{fig:dssp} and~\ref{fig:gyrate} show the colors for two different dimensions.
 
-\paragraph*{Axis sorting}
-\paragraph*{Axis reordering}
-\paragraph*{Recoloring by axis selection}
+\begin{figure}
+\includegraphics[width=1.0\linewidth]{figs/dssp.png}
+\caption{Colors of the parallel coordinates for the DSSP dimension.} 
+\label{fig:dssp}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=1.0\linewidth]{figs/gyrate.png}
+\caption{Colors of the parallel coordinates for the GYRATE dimension.} 
+\label{fig:gyrate}
+\end{figure}
 
@@
 \includegraphics[width=0.8\linewidth]{figs/radar.png}
-\caption{Example of one amino acid being visualized in the radar plot.} 
+\caption{Example of one simulation being visualized in the radar plot.} 
 \label{fig:radar}
@@
 \subsection{Slider}
-
-%==========================================
-\section{Experiments}
-%
 

### 2017-07-31 paper/paper.tex
paper

@@
 
+In a molecular dynamics simulation, many features can be measured, depending on the researcher’s interests.
+One of the mainstays of simulation analysis is the inspection of trajectory convergence, an indication of simulation stability~\cite{grossfield2007convergence}.
+It is, however, well known that convergence is a subjective matter, and that the evaluation of single structural features (such as RMSD) for this purpose is very unreliable~\cite{knapp2011intuitive}~\cite{van2006biomolecular}.
+Thus, the simultaneous evaluation of multiple structural analysis via a simple visual tool, as the one presented here, is of great utility to the field of macromolecular simulation.
+
 Proteins are polymers formed by a sequence of 20 different possible amino acids that under physiological conditions fold into a precise shape known as its native state~\cite{anfinsen:1973}.
@@
 The proposed visualization technique takes advantage of the use of three different visualization tools working in synchrony, and the capability of changing the data over time.
+The parallel coordinates and radar plot data is normalized in the range of minimum and maximum values for each dimension along all timesteps.
 
@@
 \paragraph*{Item selection} When right-clicking on a line of the grid with the mouse that line is selected and the item is fixed on the plots.
+The selected line is becomes darker on the parallel coordinates plot.
 
@@
 
-The parallel coordinates plot is used to show a global view of the data, displaying all the itens in a given time at once.
+The parallel coordinates plot is used to show a global view of the data, displaying all the itens in a given time at once and allowing the user to view the general "shape" of the simulations.
 
@@
 \paragraph*{Axis brushing} The brush is the filtering operation of the parallel coordinates and can be seen in Fig.~\ref{fig:brush}.
-Draging the mouse along an axis select the itens in that range.
+Draging the mouse along an axis select the items in that range.
 This change is reflected on the grid.
@@
 Figures~\ref{fig:dssp} and~\ref{fig:gyrate} show the colors for two different dimensions.
+This function is useful when analysing one dimension while wanting to keep in mind the behavior of another.
 
@@
 \subsection{Radar Plot}
+
+The objective of the radar plot, showed in Fig.~\ref{fig:radar}, is to visualize and compare specif items of the data, i.e., single simulations.
+The hypothesis is that overlaping the shapes of the lines from the parallel coordinates in a radial way makes it easier com see the similarities and differences between a small number of items, while the global view is better represented by the parallel coordinates plot since for many shapes the radar plot becomes convoluted.
+
 \begin{figure}
@@
 \end{figure}
-\paragraph*{Item highlighting}
+\paragraph*{Item highlighting} When hoving the mouse over a shape in the radar plot or its label, the shape is filled in order to be higlighted.
 
 \subsection{Slider}
+
+The slider is the element that allows the user to change the data being visualized over time (Fig~\ref{fig:slider}).
+It can be clicked or dragged, then selecting a specific time step of the simulation, and the plots and grid will be updated.
+It is also possible to visualize the changes in time with animations.
+For this there are two buttons, "Play" and "Rec", that update the data automatically untill the end of the timesteps.
+Interacting with any other element of the visualization pauses the animation.
+A text box informs the current timestep.
+
+\begin{figure}
+\includegraphics[width=0.8\linewidth]{figs/slider.png}
+\caption{View of the elements of the slider, that enables the change of timesteps.} 
+\label{fig:slider}
+\end{figure}
+
+%==========================================
+\section{Experiments}
+%
+
+All elements of this visualization tool were implemented using JavaScript, HTML and CSS, with the visualization library D3.js.
+The parallel coordinates plot uses the visual toolkit for multidimensional detectives Parallel Coordinates (0.7.0) (syntagmatic.github.io/parallel-coordinates).
+
+The radar plot was build from the implementations of Nadieh Bremer (https://www.visualcinnamon.com/2015/10/different-look-d3-radar-chart.html) and Micah Stubbs (https://bl.ocks.org/micahstubbs/a772306d6fd49874ec92).
 

### 2017-08-01 paper/paper.tex
paper

@@
 The data for testing this visualization tool comes from the Kappa-conotoxin PVIIA, with amino acids sequence: $CRIPNQKCFQHLDDCCSRKCNRFNKCV$.
+Its three dimensional structure, obtained with nuclear magnetic resonance (NMR) from the Protein Data Bank (PDB) under the code 1AV3, can be seen in Fig.~\ref{fig:pviia}.
 Kappa-conotoxins are neurotoxical proteins extracted from sea slugs poison.
@@
 The substitution of the asparagine ($N$) in the fifth position in the amino acids chain of the Kappa-conotoxin PVIIA by an alanine ($A$) is know to cause a reduction of 100\% in the toxicity of this protein~\cite{jacobsen2000single}~\cite{mir2016conotoxins}~\cite{akey2002inherited}.
+
+\begin{figure}
+\includegraphics[width=0.7\linewidth]{figs/pviia.png}
+\caption{Three dimensional structure of the Kappa-conotoxin PVIIA.} 
+\label{fig:pviia}
+\end{figure}
 
@@
 %==========================================
-\section{Experiments}
+\section{Experiments and Discussion}
 %
@@
 All elements of this visualization tool were implemented using JavaScript, HTML and CSS, with the visualization library D3.js.
-The parallel coordinates plot uses the visual toolkit for multidimensional detectives Parallel Coordinates (0.7.0) (syntagmatic.github.io/parallel-coordinates).
+The parallel coordinates plot uses the visual toolkit for multidimensional detectives Parallel Coordinates (0.7.0) (\url{http://syntagmatic.github.io/parallel-coordinates}).
 
-The radar plot was build from the implementations of Nadieh Bremer (https://www.visualcinnamon.com/2015/10/different-look-d3-radar-chart.html) and Micah Stubbs (https://bl.ocks.org/micahstubbs/a772306d6fd49874ec92).
+The radar plot was build from the implementations of Nadieh Bremer (\url{http://visualcinnamon.com/2015/10/different-look-d3-radar-chart.html}) and Micah Stubbs (\url{http://bl.ocks.org/micahstubbs/a772306d6fd49874ec92}).
 
-%==========================================
-\section{Results and Discussion}
-%
+As previously mentioned, the Kappa-conotoxin PVIIA was chosen as example for testing the visualization tool.
+We know from the start that the simulation containing the asparagine ($N$) in the fifth position of its amino acid chain represents the protein in its natural state.
+Also, the change of this asparagine by an alanine is reported to reduce 100\% of the proteins toxicity.
+When comparing the simulations with asparagine and alanine, thus, it would be expected to see some similarity between then, since the mutation don't destroy the protein, but also enough differences to justify the loss of function.
 
-%
+This comparison is showed in \figref{fig:alaasn} for three different moments in the simulations.
+The greatest discrepancy observed are the DSSP and RMSF attributes, what could indicate the 3D structure of the proteins have significant differences.
+
+\subimages[htb]{Comparison between the simulations with asparagine (yellow) and alanine (red) for at three different moments.}{fig:alaasn}{%
+  \subimage[Timestep 30000]{.48}{alaasn30000.png}%
+  \subimage[Timestep 40000]{.48}{alaasn40000.png}% 
+  \\
+  \subimage[Timestep 50000]{.48}{alaasn50000.png}%
+}
+
+\subimages[htb]{Comparison between the simulations with asparagine (red), glycine (yellow) and proline (blue) for at three different moments.}{fig:asnglypro}{%
+  \subimage[Timestep 30000]{.48}{asnglypro30000.png}%
+  \subimage[Timestep 40000]{.48}{asnglypro40000.png}% 
+  \\
+  \subimage[Timestep 50000]{.48}{asnglypro50000.png}%
+}
+
+\subimages[htb]{Comparison between the simulations with asparagine (red), aspartic acid (yellow) and methionine (blue) for at three different moments.}{fig:asnaspmet}{%
+  \subimage[Timestep 30000]{.48}{asnaspmet30000.png}%
+  \subimage[Timestep 40000]{.48}{asnaspmet40000.png}% 
+  \\
+  \subimage[Timestep 50000]{.48}{asnaspmet50000.png}%
+}
 
 %------------------------------------------------------------------------- 
+%==========================================
+
+\section{Conclusion}
+%
+A demo can be tested at: \url{http://inf.ufrgs.br/~bigrisci/parallel-coordinates}
+
 \subsection{Future work}
 %
+This tool, although functional, is open for further improvements.
+It would be desired to expand the synchrony between different plots and the addition of new charts that could provide new insights about the data.
 
-%==========================================
-\section{Conclusion}
-%
-A demo can be tested at: http://inf.ufrgs.br/~bigrisci/parallel-coordinates/
+A future extension of this project is to make it an available webtool allowing researchers to visualize their molecular dynamics simulation data.
+The user should be able to upload the output file generated from GROMACS and select the desired attributes.
+We hope this could help to better understandment of the simulations and comparisons between them.
+
+Another possible use for this tool, outside the field of molecular dynamics simulation, would be the visualization of convergence in population based optimization algorithms for multidimensional problems.
+This data seems to fit well within the techniques used in this project.
 
@@
 %
+I would like to thank the structural Bioinformatics and Computational Biology Lab (INF-UFRGS) for the great help generating and analysing the data for this project and testing the visualization tool.
+Special thanks to Dr.
+Marcio Dorn, Dr.
+Rodrigo Ligabue-Braun and Leonardo Alves.
 

### 2017-08-01 paper/paper.tex
paper

@@
 \begin{IEEEkeywords}
-one or two words; separated by semicolon; from specific; to generic fields;
+molecular dynamics simulation; bioinformatics; proteins; protein folding; amino acid mutation; temporal visualization; multidimensional visualization; parallel coordinates; radar chart;
 
@@
 
-Proteins are polymers formed by a sequence of 20 different possible amino acids that under physiological conditions fold into a precise shape known as its native state~\cite{anfinsen:1973}.
+Proteins are polymers formed by a sequence of around 20 different possible amino acids (Fig.~\ref{fig:aminoacids}) that under physiological conditions fold into a precise shape known as its native state~\cite{anfinsen:1973}.
 Each amino acid has an alpha carbon (\texttt{CA}) with bonds to amino (\texttt{NH2}) and carboxyl (\texttt{COOH}) groups and a variable side-chain (\texttt{R}) that determines the particular physicochemical properties of each residue.
+
+\begin{figure}
+\includegraphics[width=0.8\linewidth]{figs/Amino_Acids.png}
+\caption{Table of amino acids physicochemical properties.} 
+\label{fig:aminoacids}
+\end{figure}
+
 A peptide is a molecule composed of two or more amino acids chained by a chemical bond called the \textit{peptide bond}.
@@
 The rotation is only permitted around the bonds \texttt{N-C$\alpha$} and \texttt{C}$_{\alpha}$\texttt{-C}.
+
 The analysis of experimental protein structures (\texttt{X}-ray data) reveals that amino acid residues can assume many conformations in proteins~\cite{Borguesan:2015}.
@@
 
-\subsection{Radar Plot}
+\subsection{Radar Chart}
 
@@
 The proposed visualization technique takes advantage of the use of three different visualization tools working in synchrony, and the capability of changing the data over time.
-The parallel coordinates and radar plot data is normalized in the range of minimum and maximum values for each dimension along all timesteps.
+The parallel coordinates and radar chart data is normalized in the range of minimum and maximum values for each dimension along all time steps.
 
@@
 \end{figure}
-\paragraph*{Item highlighting} When hoving the mouse over a line in the grid, that line is highlited. This operation also reflects on the other plots.
-\paragraph*{Item selection} When right-clicking on a line of the grid with the mouse that line is selected and the item is fixed on the plots.
-The selected line is becomes darker on the parallel coordinates plot.
+\paragraph*{Item highlighting} When hoving the mouse over a line in the grid, that line is highlited. This operation also reflects on the other charts.
+\paragraph*{Item selection} When right-clicking on a line of the grid with the mouse that line is selected and the item is fixed on the charts.
+The selected line is becomes darker on the parallel coordinates chart.
 
@@
 
-The parallel coordinates plot is used to show a global view of the data, displaying all the itens in a given time at once and allowing the user to view the general "shape" of the simulations.
+The parallel coordinates chart is used to show a global view of the data, displaying all the items in a given time at once and allowing the user to view the general "shape" of the simulations and spread of the values between items.
 
@@
 This change is reflected on the grid.
-\paragraph*{Axis sorting} When double clicking an axis the order of its values is inverted. This change is reflected on the radar plot.
-\paragraph*{Axis reordering} When right-clicking an axis and draging it to left or right the axes are reordered. This change is reflected on the radar plot.
+\paragraph*{Axis sorting} When double clicking an axis the order of its values is inverted. This change is reflected on the radar chart.
+\paragraph*{Axis reordering} When right-clicking an axis and draging it to left or right the axes are reordered. This change is reflected on the radar chart.
 \paragraph*{Recoloring by axis selection} The color of the lines of the parallel coordinates is defined by the range of the selected axis.
@@
 
-\subsection{Radar Plot}
+\subsection{Radar Chart}
 
-The objective of the radar plot, showed in Fig.~\ref{fig:radar}, is to visualize and compare specif items of the data, i.e., single simulations.
-The hypothesis is that overlaping the shapes of the lines from the parallel coordinates in a radial way makes it easier com see the similarities and differences between a small number of items, while the global view is better represented by the parallel coordinates plot since for many shapes the radar plot becomes convoluted.
+The objective of the radar chart, showed in Fig.~\ref{fig:radar}, is to visualize and compare specif items of the data, i.e., single simulations.
+The hypothesis is that overlaping the shapes of the lines from the parallel coordinates in a radial way makes it easier com see the similarities and differences between a small number of items, while the global view is better represented by the parallel coordinates chart since for many shapes the radar chart becomes convoluted.
 
@@
 \includegraphics[width=0.8\linewidth]{figs/radar.png}
-\caption{Example of one simulation being visualized in the radar plot.} 
+\caption{Example of one simulation being visualized in the radar chart.} 
 \label{fig:radar}
 \end{figure}
-\paragraph*{Item highlighting} When hoving the mouse over a shape in the radar plot or its label, the shape is filled in order to be higlighted.
+\paragraph*{Item highlighting} When hoving the mouse over a shape in the radar chart or its label, the shape is filled in order to be higlighted.
 
@@
 The slider is the element that allows the user to change the data being visualized over time (Fig~\ref{fig:slider}).
-It can be clicked or dragged, then selecting a specific time step of the simulation, and the plots and grid will be updated.
+It can be clicked or dragged, then selecting a specific time step of the simulation, and the charts and grid will be updated.
 It is also possible to visualize the changes in time with animations.
-For this there are two buttons, "Play" and "Rec", that update the data automatically untill the end of the timesteps.
+For this there are two buttons, "Play" and "Rec", that update the data automatically untill the end of the time steps.
 Interacting with any other element of the visualization pauses the animation.
-A text box informs the current timestep.
+A text box informs the current time step.
 
@@
 \includegraphics[width=0.8\linewidth]{figs/slider.png}
-\caption{View of the elements of the slider, that enables the change of timesteps.} 
+\caption{View of the elements of the slider, that enables the change of time steps.} 
 \label{fig:slider}
@@
 All elements of this visualization tool were implemented using JavaScript, HTML and CSS, with the visualization library D3.js.
-The parallel coordinates plot uses the visual toolkit for multidimensional detectives Parallel Coordinates (0.7.0) (\url{http://syntagmatic.github.io/parallel-coordinates}).
+The parallel coordinates chart uses the visual toolkit for multidimensional detectives Parallel Coordinates (0.7.0) (\url{http://syntagmatic.github.io/parallel-coordinates}).
 
-The radar plot was build from the implementations of Nadieh Bremer (\url{http://visualcinnamon.com/2015/10/different-look-d3-radar-chart.html}) and Micah Stubbs (\url{http://bl.ocks.org/micahstubbs/a772306d6fd49874ec92}).
+The radar chart was build from the implementations of Nadieh Bremer (\url{http://visualcinnamon.com/2015/10/different-look-d3-radar-chart.html}) and Micah Stubbs (\url{http://bl.ocks.org/micahstubbs/a772306d6fd49874ec92}).
 
@@
 \subimages[htb]{Comparison between the simulations with asparagine (yellow) and alanine (red) for at three different moments.}{fig:alaasn}{%
-  \subimage[Timestep 30000]{.48}{alaasn30000.png}%
-  \subimage[Timestep 40000]{.48}{alaasn40000.png}% 
+  \subimage[Time step 30000]{.48}{alaasn30000.png}%
+  \subimage[Time step 40000]{.48}{alaasn40000.png}% 
   \\
-  \subimage[Timestep 50000]{.48}{alaasn50000.png}%
+  \subimage[Time step 50000]{.48}{alaasn50000.png}%
 }
 
+In another test, we can compare the simulation with asparagine to the ones with glycine and proline, as in \figref{fig:asnglypro}.
+The amino acids glycine and proline, due to their characteristics, usually interfere greatly in the structure of a protein when placed instead of another.
+
 \subimages[htb]{Comparison between the simulations with asparagine (red), glycine (yellow) and proline (blue) for at three different moments.}{fig:asnglypro}{%
-  \subimage[Timestep 30000]{.48}{asnglypro30000.png}%
-  \subimage[Timestep 40000]{.48}{asnglypro40000.png}% 
+  \subimage[Time step 30000]{.48}{asnglypro30000.png}%
+  \subimage[Time step 40000]{.48}{asnglypro40000.png}% 
   \\
-  \subimage[Timestep 50000]{.48}{asnglypro50000.png}%
+  \subimage[Time step 50000]{.48}{asnglypro50000.png}%
 }
 
+Finally, it would be of interest to identify possible mutation candidates that would interfere the least with the original protein structure and function.
+Using visual inspection (\figref{fig:asnaspmet}), the amino acids aspartic acid and methionine, based only on the simulation attributes, seem to be potential options.
+Of course, any further conclusion is depended of biological analysis, with the visualization tool serving only as a first step for insights.
+
 \subimages[htb]{Comparison between the simulations with asparagine (red), aspartic acid (yellow) and methionine (blue) for at three different moments.}{fig:asnaspmet}{%
-  \subimage[Timestep 30000]{.48}{asnaspmet30000.png}%
-  \subimage[Timestep 40000]{.48}{asnaspmet40000.png}% 
+  \subimage[Time step 30000]{.48}{asnaspmet30000.png}%
+  \subimage[Time step 40000]{.48}{asnaspmet40000.png}% 
   \\
-  \subimage[Timestep 50000]{.48}{asnaspmet50000.png}%
+  \subimage[Time step 50000]{.48}{asnaspmet50000.png}%
 }
@@
 This tool, although functional, is open for further improvements.
-It would be desired to expand the synchrony between different plots and the addition of new charts that could provide new insights about the data.
+It would be desired to expand the synchrony between different charts and the addition of new charts that could provide new insights about the data.
 

### 2017-08-02 paper/paper.tex
paper

@@
 %
+The work in~\cite{likhachev2016available} reviews some of the available instruments when analyzing molecular dynamics trajectories, including visualization tools.
+OVITO~\cite{stukowski2009visualization} is an open visualization tool for atomistic simulation data.
+TRAVIS~\cite{brehm2012travis} is a free analyzer and visualizer for Monte Carlo and molecular dynamics trajectories.
+The study in~\cite{garg2010visualization} presents a visualization tool for many tasks of molecular dynamics simulation.
+QwikMD~\cite{ribeiro2016qwikmd} is a toolkit that includes tools for analyzing simulations.
 
@@
 The data for testing this visualization tool comes from the Kappa-conotoxin PVIIA, with amino acids sequence: $CRIPNQKCFQHLDDCCSRKCNRFNKCV$.
-Its three dimensional structure, obtained with nuclear magnetic resonance (NMR) from the Protein Data Bank (PDB) under the code 1AV3, can be seen in Fig.~\ref{fig:pviia}.
+Its three dimensional structure, obtained with nuclear magnetic resonance (NMR) from the Protein Data Bank (PDB) under the code 1AV3~\cite{scanlon1997solution}, can be seen in Fig.~\ref{fig:pviia}.
 Kappa-conotoxins are neurotoxical proteins extracted from sea slugs poison.
@@
 
-\subimages[htb]{Comparison between the simulations with asparagine (yellow) and alanine (red) for at three different moments.}{fig:alaasn}{%
+\subimages[htb]{Comparison between the simulations with asparagine (yellow) and alanine (red) at three different moments.}{fig:alaasn}{%
   \subimage[Time step 30000]{.48}{alaasn30000.png}%
@@
 
-\subimages[htb]{Comparison between the simulations with asparagine (red), glycine (yellow) and proline (blue) for at three different moments.}{fig:asnglypro}{%
+\subimages[htb]{Comparison between the simulations with asparagine (red), glycine (yellow) and proline (blue) at three different moments.}{fig:asnglypro}{%
   \subimage[Time step 30000]{.48}{asnglypro30000.png}%
@@
 
-\subimages[htb]{Comparison between the simulations with asparagine (red), aspartic acid (yellow) and methionine (blue) for at three different moments.}{fig:asnaspmet}{%
+\subimages[htb]{Comparison between the simulations with asparagine (red), aspartic acid (yellow) and methionine (blue) at three different moments.}{fig:asnaspmet}{%
   \subimage[Time step 30000]{.48}{asnaspmet30000.png}%

### 2017-08-02 paper/paper.tex
paper

@@
 
-%==========================================
-\section{Technical background}
-%
-
-\subsection{Grid}
-
-\subsection{Parallel Coordinates}
-
-\subsection{Radar Chart}
-
 %------------------------------------------------------------------------- 
@@
 
-The parallel coordinates chart is used to show a global view of the data, displaying all the items in a given time at once and allowing the user to view the general "shape" of the simulations and spread of the values between items.
+The parallel coordinates chart~\cite{fanea2005interactive}~\cite{inselberg1990parallel}~\cite{inselberg1985plane} is used to show a global view of the data, displaying all the items in a given time at once and allowing the user to view the general "shape" of the simulations and spread of the values between items.
 
@@
 \end{figure}
-\paragraph*{Axis brushing} The brush is the filtering operation of the parallel coordinates and can be seen in Fig.~\ref{fig:brush}.
+\paragraph*{Axis brushing} The brush is the filtering operation of the parallel coordinates~\cite{siirtola2006interacting} and can be seen in Fig.~\ref{fig:brush}.
 Draging the mouse along an axis select the items in that range.
@@
 
-The objective of the radar chart, showed in Fig.~\ref{fig:radar}, is to visualize and compare specif items of the data, i.e., single simulations.
+The objective of the radar chart~\cite{saary2008radar}~\cite{mosley1999benchmarking}, showed in Fig.~\ref{fig:radar}, is to visualize and compare specif items of the data, i.e., single simulations.
 The hypothesis is that overlaping the shapes of the lines from the parallel coordinates in a radial way makes it easier com see the similarities and differences between a small number of items, while the global view is better represented by the parallel coordinates chart since for many shapes the radar chart becomes convoluted.
@@
 %
+
+In this paper it was presented a tool for the visual analysis of molecular dynamics simulation, focusing on the ability to compare two or more simulations.
+From the available charts it should be possible to gain insights that can inspire further investigation about the data and the biological problem in question.
+
 A demo can be tested at: \url{http://inf.ufrgs.br/~bigrisci/parallel-coordinates}
@@
 Marcio Dorn, Dr.
-Rodrigo Ligabue-Braun and Leonardo Alves.
+Rodrigo Ligabue-Braun and Leonardo Alves Santos.
 

### 2017-08-03 paper/paper.tex
paper

@@
 %
+
+Molecular dynamics simulation is a powerful tool for understanding the behavior of biomolecules such as proteins.
+When comparing the trajectory convergence of simulations, however, the researcher can face difficulties inspecting and selecting the multidimensional data.
+In this paper it is proposed a new visualization tool that combines parallel coordinates, radar chart and grid and the ability to update simulation data over time.
+The tool is tested with simulations of mutations of the Kappa-conotoxin PVIIA.
+
 \end{abstract}
@@
 %
-The work in~\cite{likhachev2016available} reviews some of the available instruments when analyzing molecular dynamics trajectories, including visualization tools.
+The work of Likhachev et al., 2016~\cite{likhachev2016available} reviews some of the available instruments when analyzing molecular dynamics trajectories, including visualization tools.
 OVITO~\cite{stukowski2009visualization} is an open visualization tool for atomistic simulation data.
 TRAVIS~\cite{brehm2012travis} is a free analyzer and visualizer for Monte Carlo and molecular dynamics trajectories.
-The study in~\cite{garg2010visualization} presents a visualization tool for many tasks of molecular dynamics simulation.
+The study of Garg, 2010~\cite{garg2010visualization} presents a visualization tool for many tasks of molecular dynamics simulation.
 QwikMD~\cite{ribeiro2016qwikmd} is a toolkit that includes tools for analyzing simulations.
@@
 \paragraph*{Item selection} When right-clicking on a line of the grid with the mouse that line is selected and the item is fixed on the charts.
-The selected line is becomes darker on the parallel coordinates chart.
+The selected line becomes darker on the parallel coordinates chart.
 
@@
 
-The objective of the radar chart~\cite{saary2008radar}~\cite{mosley1999benchmarking}, showed in Fig.~\ref{fig:radar}, is to visualize and compare specif items of the data, i.e., single simulations.
-The hypothesis is that overlaping the shapes of the lines from the parallel coordinates in a radial way makes it easier com see the similarities and differences between a small number of items, while the global view is better represented by the parallel coordinates chart since for many shapes the radar chart becomes convoluted.
+The objective of the radar chart~\cite{saary2008radar}~\cite{mosley1999benchmarking}, showed in Fig.~\ref{fig:radar}, is to visualize and compare specific items of the data, i.e., single simulations.
+The hypothesis is that overlaping the shapes of the lines from the parallel coordinates in a radial way makes it easier to see the similarities and differences between a small number of items, while the global view is better represented by the parallel coordinates chart since for many shapes the radar chart becomes convoluted.
 
@@
 All elements of this visualization tool were implemented using JavaScript, HTML and CSS, with the visualization library D3.js.
-The parallel coordinates chart uses the visual toolkit for multidimensional detectives Parallel Coordinates (0.7.0) (\url{http://syntagmatic.github.io/parallel-coordinates}).
-
-The radar chart was build from the implementations of Nadieh Bremer (\url{http://visualcinnamon.com/2015/10/different-look-d3-radar-chart.html}) and Micah Stubbs (\url{http://bl.ocks.org/micahstubbs/a772306d6fd49874ec92}).
+The parallel coordinates chart uses the visual toolkit for multidimensional detectives Parallel Coordinates (0.7.0) \footnote{\url{http://syntagmatic.github.io/parallel-coordinates}}.
+The radar chart was build from the implementations of Nadieh Bremer \footnote{\url{http://visualcinnamon.com/2015/10/different-look-d3-radar-chart.html}} and Micah Stubbs \footnote{\url{http://bl.ocks.org/micahstubbs/a772306d6fd49874ec92}}.
 
@@
 Also, the change of this asparagine by an alanine is reported to reduce 100\% of the proteins toxicity.
-When comparing the simulations with asparagine and alanine, thus, it would be expected to see some similarity between then, since the mutation don't destroy the protein, but also enough differences to justify the loss of function.
+When comparing the simulations with asparagine and alanine, thus, it would be expected to see some similarity between them, since the mutation does not destroy the protein, but also enough differences to justify the loss of function.
 

### 2017-08-03 paper/presentation.tex
presentation

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Beamer Presentation
% LaTeX Template
% Version 1.0 (10/11/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND THEMES
%----------------------------------------------------------------------------------------

\documentclass{beamer}

\mode<presentation> {

% The Beamer class comes with a number of default slide themes
% which change the colors and layouts of slides. Below this is a list
% of all the themes, uncomment each in turn to see what they look like.

%\usetheme{default}
%\usetheme{AnnArbor}
%\usetheme{Antibes}
%\usetheme{Bergen}
%\usetheme{Berkeley}
%\usetheme{Berlin}
%\usetheme{Boadilla}
%\usetheme{CambridgeUS}
%\usetheme{Copenhagen}
%\usetheme{Darmstadt}
%\usetheme{Dresden}
\usetheme{Frankfurt}
%\usetheme{Goettingen}
%\usetheme{Hannover}
%\usetheme{Ilmenau}
%\usetheme{JuanLesPins}
%\usetheme{Luebeck}
%\usetheme{Madrid}
%\usetheme{Malmoe}
%\usetheme{Marburg}
%\usetheme{Montpellier}
%\usetheme{PaloAlto}
%\usetheme{Pittsburgh}
%\usetheme{Rochester}
%\usetheme{Singapore}
%\usetheme{Szeged}
%\usetheme{Warsaw}

% As well as themes, the Beamer class has a number of color themes
% for any slide theme. Uncomment each of these in turn to see how it
% changes the colors of your current slide theme.

%\usecolortheme{albatross}
%\usecolortheme{beaver}
%\usecolortheme{beetle}
%\usecolortheme{crane}
%\usecolortheme{dolphin}
%\usecolortheme{dove}
%\usecolortheme{fly}
%\usecolortheme{lily}
%\usecolortheme{orchid}
%\usecolortheme{rose}
%\usecolortheme{seagull}
%\usecolortheme{seahorse}
%\usecolortheme{whale}
%\usecolortheme{wolverine}

%\setbeamertemplate{footline} % To remove the footer line in all slides uncomment this line
%\setbeamertemplate{footline}[page number] % To replace the footer line in all slides with a simple slide count uncomment this line

%\setbeamertemplate{navigation symbols}{} % To remove the navigation symbols from the bottom of all slides uncomment this line
}

\usepackage{graphicx} % Allows including images
\usepackage{booktabs} % Allows the use of \toprule, \midrule and \bottomrule in tables
\usepackage[brazilian]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{animate}
\usepackage{amsmath}
\DeclareMathOperator{\atantwo}{atan2}
\newcommand{\angstrom}{\textup{\AA}}

%----------------------------------------------------------------------------------------
%	TITLE PAGE
%----------------------------------------------------------------------------------------

\title[T2]{Visualização de simulações de dinâmica molecular} % The short title appears at the bottom of every slide, the full title is only on the title page

\author{Bruno Iochins Grisci} % Your name
\institute[UFRGS] % Your institution as it will appear on the bottom of every slide, may be shorthand to save space
{
Universidade Federal do Rio Grande do Sul \\ % Your institution for the title page
\medskip
\textit{bigrisci@inf.ufrgs.br} % Your email address
}
\date{\today} % Date, can be changed to a custom date

\begin{document}

\begin{frame}
\titlepage % Print the title page as the first slide
\end{frame}

\begin{frame}
\frametitle{Sumário} % Table of contents slide, comment this block out to remove it
\tableofcontents % Throughout your presentation, if you choose to use \section{} and \subsection{} commands, these will automatically be printed on this slide as an overview of your presentation
\end{frame}

%----------------------------------------------------------------------------------------
%	PRESENTATION SLIDES
%----------------------------------------------------------------------------------------

%------------------------------------------------
\section{Introdução} % Sections can be created in order to organize your presentation into discrete blocks, all sections and subsections are automatically printed in the table of contents as an overview of the talk
%------------------------------------------------

\begin{frame}
\frametitle{1AJX}
%\begin{figure}
%\includegraphics[width=0.7\linewidth]{1AJX.png}
%\end{figure}
\end{frame}

%------------------------------------------------
\section{Implementação} % Sections can be created in order to organize your presentation into discrete blocks, all sections and subsections are automatically printed in the table of contents as an overview of the talk
%------------------------------------------------

\begin{frame}
\frametitle{Ferramentas}
\begin{itemize}
\item JavaScript;
\item HTML;
\item CSS;
\item D3.js.
\end{itemize}
\end{frame}

%------------------------------------------------
\section{Ferramenta} % Sections can be created in order to organize your presentation into discrete blocks, all sections and subsections are automatically printed in the table of contents as an overview of the talk
%------------------------------------------------

\begin{frame}
\frametitle{Funcionalidades}
\begin{itemize}
\item Grid
  \begin{itemize}
  \item Destaque de item
  \item Seleção de item
  \end{itemize}
\item Parallel Coordinates
  \begin{itemize}
  \item Filtragem de eixo
  \item Ordenação de eixo
  \item Reposicionamento de eixo
  \item Coloração por seleção de eixo
  \end{itemize}
\item Radar Chart
  \begin{itemize}
  \item Destaque de item
  \end{itemize}
\item Slider
\end{itemize}
\end{frame}

%------------------------------------------------
\section{Resultados} % Sections can be created in order to organize your presentation into discrete blocks, all sections and subsections are automatically printed in the table of contents as an overview of the talk
%------------------------------------------------

%----------------------------------------------------------------------------------------

\end{document}

### 2017-08-04 paper/presentation.tex
presentation

@@
 }
-
 \usepackage{graphicx} % Allows including images
+\usepackage{subimages}
+\usepackage{media9}
 \usepackage{booktabs} % Allows the use of \toprule, \midrule and \bottomrule in tables
@@
 \begin{frame}
-\frametitle{1AJX}
-%\begin{figure}
-%\includegraphics[width=0.7\linewidth]{1AJX.png}
-%\end{figure}
+\frametitle{Proteínas}
+\begin{itemize}
+\item Proteínas são macromoléculas essenciais para o funcionamento do organismo dos seres-vivos.
+\item São formadas por uma sequência unidimensional de amino ́ácidos própria e única.
+\item Na natureza, existem 20 cadeias laterais, diferenciando os 20 amino ́ácidos básicos.
+\end{itemize}
+\begin{figure}
+\includegraphics[width=0.7\linewidth]{figs/protein.jpg}
+\caption{Estrutura das proteínas.} 
+\label{fig:protein}
+\end{figure}
+\end{frame}
+
+\begin{frame}
+\frametitle{Dinâmica Molecular}
+\begin{figure}
+    \centering
+    \includemedia[
+    width=0.6\linewidth,height=0.3375\linewidth,
+    activate=pageopen,
+    flashvars={
+        modestbranding=1 % no YT logo in control bar
+        &autohide=1 % controlbar autohide
+        &showinfo=0 % no title and other info before start
+        &rel=0 % no related videos after end
+    }
+        ]{}{https://www.youtube.com/watch?v=Aj5f0XSv0t8}
+\end{figure}
+\end{frame}
+
+\begin{frame}
+\frametitle{Dimensões}
+\begin{itemize}
+\item DSSP: estrutura secundária
+\item SASA: solvent-accessible surface area
+\item GYRATE: raio de giro
+\item ENERGY: energia total do sistema
+\item RMSF: root mean square fluctuation of atomic positions
+\end{itemize}
+Todas as dimensões são valores numéricos contínuos.
+\end{frame}
+
+\begin{frame}
+\frametitle{Kappa-conotoxin PVIIA}
+\begin{figure}
+\includegraphics[width=0.9\linewidth]{figs/lesma.jpg}
+\caption{Lesma marinha.} 
+\label{fig:lesma}
+\end{figure}
+\end{frame}
+
+\begin{frame}
+\frametitle{Kappa-conotoxin PVIIA}
+\begin{itemize}
+ \item Toxina encontrada em lesmas marinhas.
+ \item $CRIPNQKCFQHLDDCCSRKCNRFNKCV$
+ \item Mutação da asparagina (N) na quinta posição por uma alanina (A) causa perda de 100\% da toxicidade.
+\end{itemize}
+\begin{figure}
+\includegraphics[width=0.3\linewidth]{figs/pviia.png}
+\caption{Estrutura 3D da Kappa-conotoxin PVIIA.} 
+\label{fig:pviia}
+\end{figure}
 \end{frame}
@@
 
+\begin{frame}
+\frametitle{Visão geral}
+\begin{figure}
+\includegraphics[width=0.8\linewidth]{figs/all.png}
+\end{figure}
+Disponível em: \url{http://inf.ufrgs.br/~bigrisci/parallel-coordinates}
+\end{frame}
+
+\begin{frame}
+\frametitle{Comparação N x A}
+
+\subimages[htb]{Comparação entre simulações com asparagina (amarelo) e alanina (vermelho) em 3 momentos distintos.}{fig:alaasn}{%
+  \subimage[Time step 30000]{.3}{alaasn30000.png}%
+  \subimage[Time step 40000]{.3}{alaasn40000.png}% 
+  \subimage[Time step 50000]{.3}{alaasn50000.png}%
+}
+\end{frame}
+
+\begin{frame}
+\frametitle{Trabalhos futuros}
+\begin{itemize}
+\item Teste com outras proteínas;
+\item Ferramenta web;
+\item Adicionar novas visualizações;
+\item Experimentar com outros tipos de dados.
+\end{itemize}
+\end{frame}
+
+\begin{frame}
+\Huge{\centerline{Obrigado :)}}
+\end{frame}
+
 %----------------------------------------------------------------------------------------
